\hypertarget{DSGN1500}{\section{DSGN1500 - Design for a Better World}}

\large
\textcolor{turbo_purple}{\href{https://my.uq.edu.au/programs-courses/course.html?course_code=DSGN1500}{Official Page}} \\
Rating: \cstar\cstar\cstar\cstar\ostar

\normalsize
\subsection*{Description}
Designing changes circumstances for the better. In any existing context where people have a goal to change something, the factors they choose to wrangle and the ways they choose to do this help to shape their solution.
Designing almost always starts with a problem, or at least a problematic situation.
This situation sits within the context of the problem, and is affected by a range of social, economic, cultural, political, and environmental factors.
A designer notices these factors in different ways and to varying degrees depending on the problem.
Designing is a goal-directed activity, albeit with a goal that may not be clear at the outset.
As a designer begins grappling with a problem/situation they begin to think of ways it might be solved using available or to-be-discovered materials, methods, and technologies.
Ideas and judgements about how best to appropriate contextual factors to build solutions to an identified problem, using selected methods and materials, are exercised in pursuit of a/the solution.
There is often oscillation between the problem as firstly described, the contextual factors prioritised, and the means of producing a solution. Each of these oscillations is heuristic - it allows the designer to learn more about the problem in the pursuit of a solution.
Each attempt at solving the problem teaches the designer something about it and builds capacity for improving the solution.
Ideas for ways to solve problems are embedded in all kinds of histories.
Many of these ideas can be adapted in the face of a new problem in a different context.
Imagination and judgement are required to develop these adaptations.
The best ways to resolve context, materials, and methods to provide a good solution are learned over time and with practice.

\subsection*{Review}
review here
